---
#title: "word_abstract"
#author: "UNECE_ModernStats"
#date: "2024-01-28"
output: 
  officedown::rdocx_document:
    reference_docx: "abst_template.docx"

params:
  abstract_title: "AbstractTitle_PH"
  first_name: "Firstname_PH"
  last_name: "Lastname_PH"
  organisation: "Organisation_PH"
  country: "Country_PH"
  email_address: "email_PH"
  expertmeeting: "expmeetPH"
  venue: "venuePH"
  abstract: "Abstract_PH"
  eventdate: "DD MMMM YYYY"
  noticedate: "DD MMMM YYYY"
  coauthors: "coauthorsPH"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(officedown)
library(officer)
library(flextable)
library(magrittr)
ft <- fp_text(font.size = 40)
```

UNITED NATIONS ECONOMIC COMMISSION FOR EUROPE\
CONFERENCE OF EUROPEAN STATISTICIANS

[Expert Meeting on `r params$expertmeet`]{custom-style="strong"} \
`r params$eventdate`, `r params$venue`

`r notedateright = fpar(params$noticedate, fp_p = fp_par(text.align = "right"))
    
notedateright`

`r blueline = fp_par(
    padding.top = 5,
    border.top = fp_border(
      width = 2,
      color = "#548DD4",
    )
    )
    
blueline`

```{r ifcoauthors, include = FALSE}
if (!is.na(params$coauthors))  {
  coauths <- paste("; ",params$coauthors)
} else {
  coauths <- ""
}
```

# `r params$abstract_title`
`r coauths` (`r params$organisation`, `r params$country`)

[`r params$email_address`](`r params$email_address`)

`r run_linebreak()`

**_Abstract_**

`r params$abstract`